%-------------------------
% Resume
% Template by: Sourabh Bajaj (https://github.com/sb2nov/resume)
% License : MIT
%
% Edited by: Caleb Lehman (https://github.com/CalebLehman/cs-resume)
%------------------------

\documentclass[letterpaper,12pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Caleb Lehman}}
    & Email: \href{mailto:lehman.346@osu.edu}{lehman.346@osu.edu}\\
    & Mobile: +1-740-803-9339 \\
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Ohio State University}{Columbus, OH}
      {Overall GPA: 3.99}{Aug. 2016 -- May. 2020 (expected graduation)}
      \resumeItemListStart
        \resumeItem{Bachelor of Science in Computer Science}
        {3.97 GPA within major; Coursework included Algorithms, Software Development, Artificial Intelligence, and Computer Graphics.}
        \resumeItem{Bachelor of Science in Mathematics}
        {4.00 GPA within major; Coursework included Analysis, Linear Algebra, Differential Equations, Combinatorics, and Number Theory.}
        \resumeItem{Minor in Economics}
        {4.00 GPA within minor; Coursework included Microeconomics, Macroeconomics, Econometrics, and Game Theory.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Ohio Supercomputer Center}{Columbus, OH}
      {Student Programmer}{August 2019 - Current}
      \resumeItemListStart
        \resumeItem{Scientific Applications Group}
          {Install and manage various common scientific applications provided to users (\href{https://www.osc.edu/resources/available_software}{osc.edu/resources/available\textunderscore software}).}
        \resumeItem{User Support}
          {Respond to user requests for support regarding software licenses, bugs, and program optimization for use on the clusters.}
      \resumeItemListEnd

    \resumeSubheading
      {University of Chicago / Illinois Institute of Technology}{Chicago, IL}
      {Student Researcher}{May 2019 - August 2019}
      \resumeItemListStart
        \item Worked with Dr. Ioan Raicu and Dr. Kyle Chard on the development and testing of a novel task-based parallel runtime system targeted at extremely fine-grained workloads. Presented research in the ACM Student Research Competition at the conference \emph{Supercomputing 2019}.
      \resumeItemListEnd

    \resumeSubheading
      {Ohio Supercomputer Center}{Columbus, OH}
      {Student Programmer}{May 2018 - May 2019}
      \resumeItemListStart
        \item Worked in conjunction with researchers at the Byrd Polar and Climate Research center to develop the SETSM project (\href{https://github.com/setsmdeveloper/SETSM}{github.com/setsmdeveloper/SETSM}). Daily responsibilities included benchmarking and optimizing the code developed by the researchers.
      \resumeItemListEnd

    \resumeSubheading
      {Battelle Center for Mathematical Medicine}{Columbus, OH}
      {Student Researcher}{August 2015 - September 2016}
      \resumeItemListStart
        \item Worked with Dr. William Ray to develop and test RNA and protein sequence alignment algorithms.
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Scholarships and Awards}
  \resumeSubHeadingListStart
    \resumeSubItem{Merit-Based Scholarships}
      {Maximus Scholarship; CIS Undergraduate Scholarship; Goldstein Mathematics Scholarship (all received while at The Ohio State University).}
    \resumeSubItem{Dean's List}
      {Awarded in each semester that a student completes a minimum of 12 credit hours with a GPA of 3.5 or higher. Received all semesters while at The Ohio State University.}
    \resumeSubItem{OSU Rasor-Bareis-Gordon Mathematics Competition}
      {Finished 2\textsuperscript{nd}, 3\textsuperscript{rd}, 2\textsuperscript{nd}, and 2\textsuperscript{nd} in the 2014, 2015, 2016, and 2018 competitions.}
  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
   \resumeSubItem{Languages}
     {Experience with C/C++, Python, Javascript; Some familiarity with Haskell, Java, C\#}
 \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
